% LaTeX file for resume
% This file uses the resume document class (res.cls)

%thinking of trying to get the things as much as possible onto one line each so that more can be fit onto it

\documentclass[margin]{res}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textheight}{10in}

\begin{document}

\name{Matthew Francis-Landau\\[12pt]} % the \\[12pt] adds a blank line after name

%\address{{\bf Present Address} \\ Matthew Francis-Landau \\ 2700 Hearst Ave \\ Berkeley, CA 94720 \\
%        (424) 646-3355 }
\address{{\bf Permanent Address} \\ Matthew Francis-Landau \\ 6982 Verde Ridge Rd \\ Rancho Palos Verdes, CA 90275  \\
        (424) 646-3355 }
\address{{\bf Internet Addresses} \\ matthew@matthewfl.com \\ http://matthewfl.com \\ http://github.com/matthewfl }


\begin{resume}

\section{Objective}
%To have impact on a growing company who is dedicated to helping users in new ways through data analysis.
%To have a positive impact on a growing company who is dedicated to helping users through data analysis while furthering experience in professional work environments.
To participate in cutting edge research in the fields of machine learning utilizing big data.

\section{Education}
Third year undergraduate at UC Berkeley, Computer Science and Mathematics major.  Computer Science GPA: 3.7 \\
High school at California Academy of Math and Science, unweighted GPA: 3.8. \\
Completed 50 college units during high school, completed 70 units at UC Berkeley.


\section{Experience}
{\bf Software Engineer,} Balanced Payments, San Francisco CA \hfill 2013 - 2014
\begin{itemize} \itemsep -2pt
  \item Created specification and implantation for complete redesign of API.
  \item Developed machine learning and user tracking system to mitigate online credit card fraud.
  \item Created client library and documentation for interacting with API.
  \item Developed framework for reconciling bank statements with individual transactions.
\end{itemize}

{\bf Technical Intern,} Motion Picture Marine, Venice CA \hfill Summer 2011
\begin{itemize} \itemsep -2pt  % reduce space between items
  \item Developed vibration detection and elimination method using Fourier transformation and automatic PID gain adjustment.
  \item Debugged hardware and software issue relating to mass production of Perfect Horizon units.
  \item Co-authored grant to develop high school robotics program under Office of Naval Research (ONR).
  \item Designed technologies for remote internet connection and upgrades to in field units.
\end{itemize}


\section{Leadership Experience}
{\bf Project Manager,} Red Inc. \hfill 2011-2012
\begin{itemize} \itemsep -2pt
  \item Led team of 15 high schoolers to develop spherical flying robot.
  \item Manufactured custom propellers to meet size requirements of 10 inches.
  \item Produced three different technical documents: Project proposal, Proof of concept, Manual/product documentation.
\end{itemize}

%% {\bf Programming Leader,} Nerd Herd Robotics team \hfill 2010-2012
%% \begin{itemize} \itemsep -2pt
%%   \item Trained 120 students in basic robotic programming.
%%   \item Converted team from 3 different GUI programming environments to C/C++ based systems. % possibly take out the word based, to save space
%%   \item Mentored middle school students in basics of build robots for competition.
%% \end{itemize}

\section{Projects}
{\bf i-Lang} \hfill Summer 2012 to Today
\begin{itemize} \itemsep -2pt
  \item New programming language based around a function programming paradigm.
  \item Functions, classes, objects are viewed as ``anonymous,'' variables only provided a means for accessing what was previously defined.
  \item Language was designed to study paradigm of self modifying code at a level higher than assembly.
  \item Features an integrated database for ease of use when working with data.
  \item Future plans for developing network distribution system to enable working with large data sets in parallel.
\end{itemize}

{\bf JSApp.us} \hfill November 2010 to Today
\begin{itemize} \itemsep -2pt
  \item First open registration Node.js hosting platform.
  \item Features online code editor and live online testing.
% \item Enables trying the Node.js platform out quickly without installing anything.
\end{itemize}


\section{Computer \\ Skills}
   \begin{tabular}{l p{3in}}
    \underline{Highly Proficient at:} & C++, JavaScript, Python \\

    \underline{Technologies:} & Linux, Node.js, Scikit-Learn, SQLAlchemy, JSON Schema, PostgreSQL, Tokyo Tyrant, Arduino, Mbed, Mathematica, Hadoop, Java, \LaTeX
 \end{tabular}

\end{resume}
\end{document}
